Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-11-23 paper/paper.tex
And another layout, replacing the selected axons from the NT vs RC graph

The retinal ablation shown in Fig.\,\ref{f:chsurg}D is also unsuccessful, with
the axons from the surviving nasal retina (the transverse half was removed)
failing to arrange themselves across the entire tectum, due to the pure
`position specification' which the dual gradient model achieves. Similarly,
the tectal ablation simulation fails to reproduce experimentally observed
results in which the retinal map `squashes up' within the remaining tectal
region. Instead, axons from the transverse retina arrange with normal spacing
and axons from the nasal retina are pushd to the caudal-most side of the
remaining tectum (Fig.\,\ref{f:chsurg}E). A similar result occurs in the
mismatch experiment (Fig.\,\ref{f:chsurg}F), but in this case there are no
axons from teh transverse retina, which was been ablated and only the axons
from the nasal retina are present, arranged in a line.

>>>>

The retinal ablation shown in Fig.\,\ref{f:chsurg}D is also unsuccessful, with
the axons from the surviving nasal retina (the transverse half was removed)
failing to arrange themselves across the entire tectum, due to the pure
`position specification' which the dual gradient model achieves. Similarly,
the tectal ablation simulation fails to reproduce experimentally observed
results in which the retinal map `squashes up' within the remaining tectal
region. Instead, axons from the transverse retina arrange with normal spacing
and axons from the nasal retina are pushed to the caudal-most side of the
remaining tectum (Fig.\,\ref{f:chsurg}E). A similar result occurs in the
mismatch experiment (Fig.\,\ref{f:chsurg}F), but in this case there are no
axons from teh transverse retina, which was been ablated and only the axons
from the nasal retina are present, arranged in a line.
